---
title: "Variables and Reserved Words in R"
description: |
   In this article, you will learn about what are variables?, how to create them? the naming convention of varibales in R programming. I'll also mention some reserved keywords which can not be a variable name. 
preview: inset_plot.png
author:
  - name: Jubayer Hossain
    url: https://www.linkedin.com/in/jubayer28/
    affiliation_url: https://www.jhossain.me

date: 09-26-2020
categories:
  - R Basics
output:
  distill::distill_article:
    self_contained: false
draft: false 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Variables(Identifiers) in R
Variables are used to **store data**, whose value can be changed according to our need. Unique name given to variable (function and objects as well) is **identifier**

## Rules for writing Identifiers in R
- Identifiers can be a combination of letters, digits, period (.) and underscore (_).
- It must start with a letter or a period. If it starts with a period, it cannot be followed by a digit.
- Reserved words in R cannot be used as identifiers.

Basically, there are 5 naming conventions 

- alllowercase: e.g. `myname`
- period.separated: e.g. `new.name`
- underscore_separated: e.g. `my_name`
- lowerCamelCase: e.g. `myName`
- UpperCamelCase: e.g. `MyName`

## Creating Variables 
- Using equal(`=`) operator

```{r}
x = 10 
```
- Using leftward(`<-`) operator 

```{r}
y <- 15  
```

- Using rightward(`->`) operator 

```{r}
z <- 20 
```

## Printing Variables 
The values of the variables can be printed using `print()` or `cat()` function. The `cat()` function combines multiple items into a continuous print output.

```{r}
x = 10 
print(x)
```

```{r}
y <- 15  
cat(y)
```

```{r}
z <- 20  
z
```

## Basic Commands 
Listing variables in workspace using `ls()` and `objects()`

```{r}
ls() 
```
```{r}
objects()
```

##  Reserved Words in R 
Don't use any reserved keyword as variable name. List all of reserved words in R by using (`?Reserved`). 

The reserved words in R's parser are

- `if` `else` `repeat` `while` `function` `for` `in` `next` `break`
- `TRUE` `FALSE` `NULL` `Inf` `NaN` `NA` `NA_integer_ NA_real_ NA_complex_ NA_character_`

